### 2018-11-29 2018_nips_vigil_poster/main.tex
Small precision.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% macros for the equations
\newcommand{\cw}{\mathbf{cw}}
\newcommand{\cc}{\mathbf{c}}
\newcommand{\kb}{\mathbf{k}}
\newcommand{\mem}{\mathbf{m}}
\newcommand{\rr}{\mathbf{r}}

\newcommand{\vm}[1]{\textcolor{red}{VM: #1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

	\begin{itemize}
		\compresslist
	    \item[$\bullet$] Taking the MAC cell equations as a whole, consecutive linear layers (with no activation in-between) can be combined as one linear layer.
		\item[$\bullet$] We assume that dimension-preserving linear layers are invertible so as to avoid information loss. \vm{To reformulate?}
    \end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% macros for the equations
\newcommand{\cw}{\mathbf{cw}}
\newcommand{\cc}{\mathbf{c}}
\newcommand{\kb}{\mathbf{k}}
\newcommand{\mem}{\mathbf{m}}
\newcommand{\rr}{\mathbf{r}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

	\begin{itemize}
		\compresslist
	    \item[$\bullet$] Taking the MAC cell equations as a whole, consecutive linear layers (with no non-linear activation in-between) can be combined as one linear layer.
		\item[$\bullet$] We assume that dimension-preserving linear layers are invertible so as to avoid information loss.
    \end{itemize}
